Evidence for a Color Parameter Unassociated With Dust Within the Type~Ia Supernovae of the Nearby Supernova Factory

### 2017-02-01 apj.tex
rework dust stuff

The  strong correlation between $EW_{Ca}$ and $\lambda_{Si}$ is not surprising.   Si~II velocities have been
suggested as being able to distinguish two distinct SN~Ia populations
\citep{2009ApJ...699L.139W, 2013Sci...340..170W}.  CaII~H\&K, and more cleanly CaII~NIR photospheric features
(and 
high-velocity features if present), have been found to trend with light-curve shape  \citep{2012MNRAS.426.2359M}.
\citet{2014MNRAS.437..338C, 2014MNRAS.444.3258M} found a strong correlation between Si~II velocities and the
CaII~NIR photometric velocity feature, and found that the correlation is sensitive to the presence of high-velocity features.

@@

The range of SiII$\lambda$4130 equivalent widths is $\pm 20$~\AA\ whereas the width of the $B$-band is 851~\AA, so that its affect on magnitude
is
$2.5 \log{(20/850)} \sim 0.03$ mag.  
The implied span in $B$ magnitude based on $\beta_B$ is 0.54~mag.  Therefore $\beta_B$ cannot wholly be attributed to the flux deficit
from the line itself.
Similarly, the CaII H\&K equivalent widths have range $\pm 50$~\AA, while the width of the $U$ band is
701~\AA, so that its affect on magnitude
is
$2.5 \log{(50/701)} \sim 0.08$ mags.   The implied span in $U$ magnitude is  0.21~mag, so $\alpha_U$ cannot be completely due to the line itself.

\subsection{The Two Extrinsic Parameters $k_0$ and $k_1$}
\color{blue}
The two sets of  $\gamma^i$ parameters  are significantly non-zero. 
None of the 20000 links of 
our Monte Carlo chains for $\gamma$ exceed 0 (see Figures~\ref{global1:fig}--\ref{global5:fig}), we thus claim detection of the
influence of $k_0$ and $k_1$  on supernova magnitudes
with probability $(1-5\times 10^{-5})$.

@@

Nevertheless, we are able to examine aggregate properties of the extinction.  The extrinsic extinction and color relation can be
rearranged as
$$A_X(k_0,k_1) = R^T_V \left( A_B(k_0,k_1) -  A_V(k_0,k_1)\right) -R^T_V \left(A_B(k^0_0,k^0_1) + A_V(k^0_0,k^0_1)\right)+  A_X(k^0_0,k^0_1) .
$$
Making the assumption that it is the same for all supernovae ,
 $R^T_V$  can be determined as the slope of the linear relation between $A_X$ and $E(B-V)$.

Figure~\ref{avebv:fig} shows the relationship between $A_V$ and $E(B-V)$.
The full set of supernovae does not coincide with the expectations of a single linear law; rather the supernova population is peaked
on a ridge line, with a tail distributed below.  That is, for a fixed color excess, the amount of $V$-band extinction is bounded above
but can have values that extend toward lower values.
The assumption of a constant $R^T_V$ is not altogether correct; still we perform a linear fit that gives a slope of
%----- fitz11.py
$R^T_V=2.77 \pm 0.08$,
%----
where the uncertainty is the $68$\% credible interval and does not include goodness
 of fit.

%\begin{comment}
%\color{blue}
%Our model alone cannot determine $R^T_V = A^T_V/E^T(B-V)$ for individual objects, as $k_0^0$ and $k_1^0$ are unconstrained.
%For a qualitative view, we choose zeros  such that the $V$-band extinction and color-excess of the bluest supernova roughly correspond to $E(B-V)=0$,
%$A_V=0$, and such that the ridge line 
%has close to constant $R^T_V$.
%\color{black}
%With this ansatz, we
%estimate $R^T_V$ per supernova shown in Figure~\ref{avebv:fig}, with the expectations of the
% \citet{1999PASP..111...63F} (hereafter referred to as \citetalias{1999PASP..111...63F})  model for fixed $R^F_V$ overplotted.
%With this choice of zeropoints, the ridge line corresponds to $R_V^F\lesssim 2.5$, and even lower values of $R_V^F$ below the ridge line.
%We emphasize that the shape of the locus in this plot (though not the relative positions of the points)  and the flatness
%of the ridge line is specific to our choice of zeropoints, and that our model does not specify the zeropoints.
%A specification of per-supernova $R_V$ requires a model that can identify supernovae that suffer no extrinsic effects,
%for example by modeling  a constraining distribution for the extrinsic parameters \citep{2016arXiv160904470M}.
%\color{black}
%
\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=5.2in]{output11/avebv.pdf}
   %\includegraphics[width=2.8in]{output11/rv.pdf}
   \caption{
   $A_V$ versus $E(B-V)$, and the slope $R_V$ of the linear fit to the data.
   %Right: Shown for qualitative purposes,
   %$R^T_V=A^T_V/E^T(B-V)$ 
   %versus $E^T(B-V)$ for the supernova sample, given an ansatz for the definition of an intrinsic supernova. 
   %Overplotted is the mean and standard deviation of those points in equally divided bins.
   Overplotted the expected values for the \citetalias{1999PASP..111...63F} model
   for specific choices of $R^F$. Note that these lines are not straight, which is apparent when comparing to the straight black $R_V=2.78$ line.
   \label{avebv:fig}}
\end{figure}
%\end{comment}

@@

The 2-parameter linear model
\begin{equation}
A_X = a(X)  A_V + b(X) E(B-V)
\label{f99:eqn}
\end{equation}
approximately describes dust models.
For the case of
$R^F=2.5$ and $A^F_V=0.1$,
and the measurement of the SALT2
\citet{2007A&A...466...11G} $s=1$, $x_1=0$ SN~Ia template at $B$-band peak, the \citetalias{1999PASP..111...63F} model
gives
$a(U,B,V,R,I)=\{0.96,   1.00,   1.00,   0.97,   0.77\}$ and $b(U,B,V,R,I)=\{  1.77,   0.98,   0.12,  -0.50,  -0.53\}$.
The $F$ superscript is added to distinguish \citetalias{1999PASP..111...63F} parameters.
Over the ranges of
 $R^F$ and $A^F_V$,
and the wavelengths under consideration,  the values $a$ and $b$ change but only by $<5$\%.

Our model can be expressed as
\begin{equation}
A_X = \frac{\gamma^0_X}{\gamma^0_B-\gamma^0_V}  E_{\gamma^0}(B-V) +  \frac{\gamma^1_X}{\gamma^1_B-\gamma^1_V}  E_{\gamma^1}(B-V).
\end{equation}
Our median-fit values for the $\gamma$ coefficients,
%---- fitz11.py
$\frac{\gamma^0_X}{\gamma^0_B-\gamma^0_V}  =\{4.80 ,   3.89,   2.89,   2.22,   1.59\}$ and
$ \frac{\gamma^1_X}{\gamma^1_B-\gamma^1_V}=\{-3.83 ,  -4.42,  -5.42,  -5.15,  -4.71\}$,
%----
can be transformed to a basis composed of the $a(X)$ and $b(X)$ vectors plus a residual vector perpendicular to $a$ and $b$.
The result is
\begin{equation}
\begin{pmatrix}
 \frac{\gamma^0_X}{\gamma^0_B-\gamma^0_V} \\
\frac{\gamma^1_X}{\gamma^1_B-\gamma^1_V} 
\end{pmatrix}=
\begin{pmatrix}
\begin{array}{rr}
1.15 & 2.82 \\
0.72 & -5.27
\end{array}
\end{pmatrix} 
\begin{pmatrix}
a(X) \\
b(X)
\end{pmatrix}+
\begin{pmatrix}
\vec{\epsilon}_a \\
\vec{\epsilon}_b
\end{pmatrix},
\end{equation}
where the two residual vectors
\begin{align}
\vec{\epsilon}_a &=\{0.06, -0.07, -0.07,  0.07, 0.02\}, \\
\vec{\epsilon}_b & =\{-0.06, 0.16, -0.22, 0.33, -0.26\}
\end{align}
contribute  2\% and 5\% respectively to the total  length of the $\gamma$ vectors.
This result indicates that
the allowed variation in $UBVRI$ allowed by the \citetalias{1999PASP..111...63F} model and our best-fit model are closely aligned.

The above result is visualized in Figure~\ref{plane:fig}, which  shows two perspectives (left and right columns) of $UVI$- (top row) and $BVR$- (bottom row) spaces
of the vectors corresponding to $\gamma_X/(\gamma_B-\gamma_V)$ of our model (solid lines),
and $a(X)$, $b(X)$ of the \citetalias{1999PASP..111...63F} model (dashed lines).  
The two perspectives show that while the four vectors point in different directions for each band combination,
they are almost coplanar in $UVI$, and close to coplanar in $BVR$.

@@

A prior that $k_0$ and  $k_1$ be uncorrelated was enforced to break degeneracies in our linear models, and determines the choice of directions of
the vectors $\gamma^0$ and $\gamma^1$.  Suppose that that the data were described by a dust model.  A \citetalias{1999PASP..111...63F}  dust model 
can be written as 
%To see how this prior would operate on dust models, consider that themodel in Eqn.~\ref{f99:eqn} can
%be expressed in terms of new basis vectors parametrized by $\kappa$:
\begin{equation}
A_X =  (1-\kappa_1 \kappa_2)^{-1} [(A^F_V - \kappa_2 E^F(B-V))\left(a(X)+\kappa_1 b(X) \right) +  (-\kappa_1 A^F_V + E^F(B-V)) (\kappa_2 a(X) + b(X))],
\end{equation}
with the parameters $\kappa_1$ and $\kappa_2$ providing freedom in the directions of the two basis vectors.  In the analysis,
the $\kappa$'s are specified by the  prior of  
zero covariance between $(A^F_V - \kappa_2 E^F(B-V))$ and  $(-\kappa_1 A^F_V + E^F(B-V))$.
The preferred values for $\kappa$ are shown qualitatively in
Figure~\ref{plane:fig}.  For $\kappa_1=1/2.4$, $\kappa_2=-6.8$
the vector $\gamma^0_X$ is  aligned with 
the dust vector $\left(a(X)+\kappa_1 b(X) \right)$  and $\gamma^1_X$
is aligned with $(\kappa_2 a(X) + b(X))$  $UVI$-space.  Slightly shifted values of $\kappa_1=1/2.6$, $\kappa_2=-6.1$ apply in $BVR$-space.

To gain an intuitive understanding of $\kappa_1$, consider the hypothetical case where
all supernovae experience dust with the same $R^F$.   The zero-covariance
prior would be satisfied by  $\kappa_1=1/R^F$ and any arbitrary $\kappa_2$.
The combination  $\gamma^0_V k_0$ would correspond to  $A^F_V$.  Both $k_1=0$  and $\gamma^1$ would be unconstrained.
A slight relaxation away from the constant $R^F$ assumption would result in $\kappa_2$ no longer being arbitrary but determined by the prior, and a
non-zero $k_1$ and a $\gamma^1$.

Given the association of  our parameter $\gamma^0_V k_0$ with the $A^F_V$ of an $R^F \sim 1/\kappa_1$ dust model,
the former's distribution can be compared to the expectation for the latter.
Figure~\ref{k0_med:fig} shows the histogram of
median values of $\gamma^0_V k_0$.
The distribution is non-Gaussian, having a sharp rise in the blue and an extended tail in the red, consistent
with the expectation of dust considering the spatial distribution of supernovae within galaxies and the distribution of galaxy orientations with respect to the observer \citep{1998ApJ...502..177H}.

Figure~\ref{k0_med:fig} also shows the distribution of $\gamma^1_V k_1$, which is associated with 
extinction corrections due to deviations away from the canonical $R^F$ value.   The distribution has a long
negative tail and is peaked at its positive edge, and by construction has a mean of zero.
The implication is that while the bulk of supernovae have positive values associated with $R>1/\kappa_1$, there is a tail
of negative values associated with $R<1/\kappa_1$.  The plot of   $\gamma^0_V k_0$ versus $\gamma^1_V k_1$  shown in Figure~\ref{kk:fig} shows that
the positive edge in $\gamma^1_V k_1$ persists over the full range of  $\gamma^0_V k_0$. On the other hand, lower values of $\gamma^1_V k_1$
occur at larger values of  $\gamma^0_V k_0$.
These findings are consistent with previous results:
\citet{2014ApJ...789...32B, 2015MNRAS.453.3300A} deduce a wide range of dust behavior $1.5<R^F<3$ encountered by the SN~Ia population.
\citet{2011ApJ...729...55F} and the above authors
find that supernovae with large extinction 
preferentially exhibit low $R^F$.

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=2.8in]{output11/gamma0_med.pdf}
   \includegraphics[width=2.8in]{output11/gamma1_med.pdf}
      \caption{ Histogram of
median values of Left: $\gamma^0_V k_0$, which is associated with the $A^F_V$ of an $R^F \sim 2.4$ dust model; Right: $\gamma^1_V k_1$,
which  is associated with $\left( E^F(B-V) - \frac{ A_V^F}{2.4}\right)$, i.e.\
extinction corrections due to deviations away from the $R=2.4$ value.
   \label{k0_med:fig}}
\end{figure}

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=5.2in]{output11/kk.pdf}
      \caption{ $\gamma^0_V k_0$ versus $\gamma^1_V k_1$.
   \label{kk:fig}}
\end{figure}
%
%The model parameters $E_{\gamma^0}(B-V)$ and  $E_{\gamma^1}(B-V)$ for the supernovae in our sample
%are projected onto the  \citetalias{1999PASP..111...63F} values of $E^F(B-V)$ and $A^F$, up to an additive constant:  these are shown in Figure~\ref{avebv:fig}.
%The points are confined to a tight locus around a line, with slope that corresponds to $R^F_V=2.24 \pm 0.16$.  
%The linear fit also produces the zeropoint, allowing us to determine individual $R^F_V$ for all supernovae,
%which are shown in Figure~\ref{avebv_synth:fig}.   The relative values of the projected parameters are similar to
%the native $R_V$, $A_V$, and $E(B-V)$  shown in Figure~\ref{avebv:fig}.
%
%\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
%   \centering
%   \includegraphics[width=2.8in]{output11/avebv_synth.pdf}
%   \includegraphics[width=2.8in]{output11/avrv_synth.pdf}
%    \caption{Left: Projections of our model parameters $E_{\gamma^0}(B-V)$ and  $E_{\gamma^1}(B-V)$ for the supernovae in our sample
%onto the  \citetalias{1999PASP..111...63F} dust-model plane.  Note that the error bars do not capture the strong
%covariance between the parameters. Right: $R^F_V$ for each supernova.
%   \label{avebv_synth:fig}}
%\end{figure}
%

>>>>

\color{red}
[Greg asked for discussion but I think the spectral correlations should go in Chotard et al.\ 2017.]
The  strong correlation between $EW_{Ca}$ and $\lambda_{Si}$ is not surprising.   Si~II velocities have been
suggested as being able to distinguish two distinct SN~Ia populations
\citep{2009ApJ...699L.139W, 2013Sci...340..170W}.  CaII~H\&K, and more cleanly CaII~NIR photospheric features
(and 
high-velocity features if present), have been found to trend with light-curve shape  \citep{2012MNRAS.426.2359M}.
\citet{2014MNRAS.437..338C, 2014MNRAS.444.3258M} found a strong correlation between Si~II velocities and the
CaII~NIR photometric velocity feature, and found that the correlation is sensitive to the presence of high-velocity features.
\color{black}

@@

The range of SiII$\lambda$4130 equivalent widths is $\pm 20$~\AA\ whereas the width of the $B$-band is 851~\AA, so that its direct affect on magnitude
is
$2.5 \log{(20/850)} \sim 0.03$ mag.  
The implied span in $B$ magnitude based on $\beta_B$ is 0.54~mag.  Therefore $\beta_B$ cannot wholly be attributed to the flux deficit
from the line itself.
Similarly, the CaII H\&K equivalent widths have range $\pm 50$~\AA, while the width of the $U$ band is
701~\AA, so that its direct affect on magnitude
is
$2.5 \log{(50/701)} \sim 0.08$ mags.   The implied span in $U$ magnitude is  0.21~mag, so $\alpha_U$ cannot be completely due to the 
presence of the line itself.

\subsection{The Two Extrinsic Per-Supernova Parameters $k_0$ and $k_1$}
\color{blue}
The two sets of  $\gamma^i$ parameters  are significantly non-zero. 
None of the 20000 links of 
our Monte Carlo chains for $\gamma$ extend to 0 (see Figures~\ref{global1:fig}--\ref{global5:fig}), we thus claim detection of the
influence of $k_0$ and $k_1$  on supernova magnitudes
with probability $1-5\times 10^{-5}$.

@@

Nevertheless, we are able to examine aggregate properties of the extinction.  The extrinsic extinction and color relation can be
rearranged as
\begin{equation}
A_X(k_0,k_1) = R^T_V \left( A_B(k_0,k_1) -  A_V(k_0,k_1)\right) -R^T_V \left(A_B(k^0_0,k^0_1) + A_V(k^0_0,k^0_1)\right)+  A_X(k^0_0,k^0_1) .
\end{equation}
Making the assumption that $R^T_V$ is the same for all supernovae,
its value can be determined as the slope of the linear relation between $A_X$ and $E(B-V)$.

Figure~\ref{avebv:fig} shows the relationship between $A_V$ and $E(B-V)$.
The full set of supernovae does not coincide with the expectations of a single linear relation; rather the supernova population is peaked
on a ridge line, with a tail distributed below.  That is, for a fixed color excess, the amount of $V$-band extinction is bounded above
but can have values that extend toward lower values.
The assumption of a constant $R^T_V$ is not altogether correct; still we perform a linear fit that gives a slope of
%----- fitz11.py
$R^T_V=2.77 \pm 0.08$,
%----
where the uncertainty is the $68$\% credible interval and does not include model error.

%\begin{comment}
%\color{blue}
%Our model alone cannot determine $R^T_V = A^T_V/E^T(B-V)$ for individual objects, as $k_0^0$ and $k_1^0$ are unconstrained.
%For a qualitative view, we choose zeros  such that the $V$-band extinction and color-excess of the bluest supernova roughly correspond to $E(B-V)=0$,
%$A_V=0$, and such that the ridge line 
%has close to constant $R^T_V$.
%\color{black}
%With this ansatz, we
%estimate $R^T_V$ per supernova shown in Figure~\ref{avebv:fig}, with the expectations of the
% \citet{1999PASP..111...63F} (hereafter referred to as \citetalias{1999PASP..111...63F})  model for fixed $R^F_V$ overplotted.
%With this choice of zeropoints, the ridge line corresponds to $R_V^F\lesssim 2.5$, and even lower values of $R_V^F$ below the ridge line.
%We emphasize that the shape of the locus in this plot (though not the relative positions of the points)  and the flatness
%of the ridge line is specific to our choice of zeropoints, and that our model does not specify the zeropoints.
%A specification of per-supernova $R_V$ requires a model that can identify supernovae that suffer no extrinsic effects,
%for example by modeling  a constraining distribution for the extrinsic parameters \citep{2016arXiv160904470M}.
%\color{black}
%
\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=5.2in]{output11/avebv.pdf}
   %\includegraphics[width=2.8in]{output11/rv.pdf}
   \caption{
   $A_V$ versus $E(B-V)$, and the slope $R_V$ of the linear fit to the data.
   %Right: Shown for qualitative purposes,
   %$R^T_V=A^T_V/E^T(B-V)$ 
   %versus $E^T(B-V)$ for the supernova sample, given an ansatz for the definition of an intrinsic supernova. 
   %Overplotted is the mean and standard deviation of those points in equally divided bins.
   Overplotted are the expected curves for the \citetalias{1999PASP..111...63F} model
   for specific choices of $R^F$. Note that these lines are not straight, which is apparent when comparing to the straight black $R_V=2.78$ line.
   \label{avebv:fig}}
\end{figure}
%\end{comment}

@@

The 2-parameter linear model
\begin{equation}
A_X = a(X)  A_V + b(X) E(B-V)
\label{f99:eqn}
\end{equation}
approximately describes dust models.
For the case of
$R^F=2.5$ and $A^F_V=0.1$,
and the measurement of the SALT2
\citet{2007A&A...466...11G} $s=1$, $x_1=0$ SN~Ia template at $B$-band peak, the \citetalias{1999PASP..111...63F} model
gives
$a(U,B,V,R,I)=\{0.96,   1.00,   1.00,   0.97,   0.77\}$ and $b(U,B,V,R,I)=\{  1.77,   0.98,   0.12,  -0.50,  -0.53\}$.
The $F$ superscript is added to distinguish \citetalias{1999PASP..111...63F} parameters.
Over the ranges of
 $R^F$ and $A^F_V$,
and the wavelengths under consideration,  the values of the elements of $a$ and $b$ change but only by $<5$\%.

Our model can be expressed as
\begin{equation}
A_X = \frac{\gamma^0_X}{\gamma^0_B-\gamma^0_V}  E_{\gamma^0}(B-V) +  \frac{\gamma^1_X}{\gamma^1_B-\gamma^1_V}  E_{\gamma^1}(B-V).
\end{equation}
Our median-fit values for the $\gamma$ coefficients,
%---- fitz11.py
$\frac{\gamma^0_X}{\gamma^0_B-\gamma^0_V}  =\{4.80 ,   3.89,   2.89,   2.22,   1.59\}$ and
$ \frac{\gamma^1_X}{\gamma^1_B-\gamma^1_V}=\{-3.83 ,  -4.42,  -5.42,  -5.15,  -4.71\}$,
%----
can be transformed to a basis composed of the $a(X)$ and $b(X)$ vectors plus a residual vector perpendicular to $a$ and $b$.
The result is
\begin{equation}
\begin{pmatrix}
 \frac{\gamma^0_X}{\gamma^0_B-\gamma^0_V} \\
\frac{\gamma^1_X}{\gamma^1_B-\gamma^1_V} 
\end{pmatrix}=
\begin{pmatrix}
\begin{array}{rr}
1.15 & 2.82 \\
0.72 & -5.27
\end{array}
\end{pmatrix} 
\begin{pmatrix}
a(X) \\
b(X)
\end{pmatrix}+
\begin{pmatrix}
\vec{\epsilon}_a \\
\vec{\epsilon}_b
\end{pmatrix},
\end{equation}
where the two residual vectors
\begin{align}
\vec{\epsilon}_a &=\{0.06, -0.07, -0.07,  0.07, 0.02\}, \\
\vec{\epsilon}_b & =\{-0.06, 0.16, -0.22, 0.33, -0.26\}
\end{align}
contribute  2\% and 5\% respectively to the total  length of the $\gamma$ vectors.

This result indicates that
the allowed variation in $UBVRI$ allowed by the \citetalias{1999PASP..111...63F} model and our best-fit model are closely aligned.
That is to say, with no prior assumptions of dust extinction behavior or the distribution of $A_V$, the supernova data themselves exhibit
2-dimensional color variations that are closely aligned with the 2-dimensional color variations predicted by  \citetalias{1999PASP..111...63F} dust.

The above result is visualized in Figure~\ref{plane:fig}, which  shows two perspectives (left and right columns) of $UVI$- (top row) and $BVR$- (bottom row) spaces
of the vectors corresponding to $\gamma_X/(\gamma_B-\gamma_V)$ of our model (solid lines),
and $a(X)$, $b(X)$ of the \citetalias{1999PASP..111...63F} model (dashed lines).  All $\gamma$ vectors are chosen to intersect the origin.
The two perspectives show that while the four vectors point in different directions for each band combination,
they are almost coplanar in $UVI$, and close to coplanar in $BVR$.  The $a$ and $b$ vectors and the $\gamma^0$ and $\gamma^1$
vectors are bases for almost the same plane in the 5-dimensional color space, and can be transformed between themselves through rotation.

@@

When fixing the origin of the $\gamma$'s to zero, the are found to be coplanar with $a$ and $b$.
However the linear model does not specify zero dust so the origin of gamma is unspecified.
The general result is that the magnitude planes of the linear and dust models are parallel.
Color changes are consistent between the two models but there is no specification of the relation between $k^0$ and $k^1$ with $A_V$ and $E(B-V)$.

A prior that $k_0$ and  $k_1$ be uncorrelated was enforced to break degeneracies in our linear models, and determines the choice of directions of
the vectors $\gamma^0$ and $\gamma^1$.  Suppose that that the data were described by a dust model.  A \citetalias{1999PASP..111...63F}  dust model 
can be written as 
%To see how this prior would operate on dust models, consider that themodel in Eqn.~\ref{f99:eqn} can
%be expressed in terms of new basis vectors parametrized by $\kappa$:
\begin{equation}
A_X =  (1-\kappa_1 \kappa_2)^{-1} [(A^F_V - \kappa_2 E^F(B-V))\left(a(X)+\kappa_1 b(X) \right) +  (-\kappa_1 A^F_V + E^F(B-V)) (\kappa_2 a(X) + b(X))],
\end{equation}
with the parameters $\kappa_1$ and $\kappa_2$ providing freedom in the directions of the two basis vectors.
The vector $a(X)+\kappa_1 b(X)$ represents extinction that can occur with fixed $R^F_0=1/\kappa_1$ and unconstrained $\kappa_2$.
%While a similar interpretation could be made of $\kappa_2 a(X) + b(X)$, note that to first order the extinction for $\Delta R$
%perturbations from a fixed $R^F_0$ is
%\begin{equation}
%A_X = A_V \left(a(X) + \left(\frac{1}{R^F_0} - \frac{\Delta R^F}{R^F_0} \right) b(X) \right).
%\end{equation}
%Then $\kappa^{-1}_2$ can this be associated with $\frac{1}{R^F_0} - \frac{\Delta R^F}{R^F_0}$.

The preferred values for $\kappa$ are shown qualitatively in
Figure~\ref{plane:fig}.  For $\kappa_1=1/2.4$, $\kappa_2=-6.8$
the vector $\gamma^0_X$ is  aligned with 
the dust vector $a(X)+\kappa_1 b(X)$  and $\gamma^1_X$
is aligned with $\kappa_2 a(X) + b(X)$  $UVI$-space.  
%With these values of $\kappa$, the dust parameters are $R^F_0=2.4$ and $\Delta R^F=1.4$.
Slightly shifted values of $\kappa_1=1/2.6$, $\kappa_2=-6.1$ apply in $BVR$-space.
%, which correspond to  $R^F_0=2.6$ and $\Delta R^F=1.4$.

To gain an intuitive understanding of how the $\kappa$ values are determined, consider the hypothetical case where
all supernovae experience dust with the same $R^F$.   There is only one free parameter $A^F_V$ and magnitudes are
constrained to move along the vector $a(X)+b(X)/R^F$.  In the fit of the linear model, the zero-covariance condition is satisfied when
$-\kappa_1 A^F_V + E^F(B-V)=0$,  i.e.\ when $\kappa_1=1/R^F$.  
Supernova magnitudes do not vary along the $\kappa_2 a(X) + b(X)$ direction.  Consequently
$\gamma^0$ is aligned with  $a(X)+b(X)/R^F$, and $\gamma^1$ is unconstrained.

Now consider what happens when supernovae can have small  perturbations away from that constant $R^F$ value.  Each supernova magnitude
can be described as the sum of the contribution along the $a(X)+b(X)/R^F$ direction, plus a perturbation in a different direction due its deviation  from $R_V$.
The zero-correlation condition, which determines the direction of $\gamma^1$,  is for the coordinate values along $\gamma^0$ to be uncorrelated with the coordinate values along $\gamma^1$.
Our analysis yields an angle of 154\arcdeg between  $\gamma^0$ and $\gamma^1$.
The vectors not being perpendicular arises because the distribution of the perturbations in $R^F$ are dependent on the amount of first-order $R_V$ extinction.

Given the association of  our parameter $\gamma^0_V k_0$ with changes in $A^F_V$ of an $R^F =\kappa^{-1}_1$ dust model up to an additive offset,
the former's distribution can be compared to the expectation for the latter.
Figure~\ref{k0_med:fig} shows the histogram of
median values of $\gamma^0_V k_0$.
The distribution is non-Gaussian, having a sharp rise in the blue and an extended tail in the red.  This is consistent
with the expectation of dust considering the spatial distribution of supernovae within galaxies and the distribution of galaxy orientations with respect to the observer \citep{1998ApJ...502..177H}.  This distribution is given by the data, in that it is independent of any knowledge or prior
for the distribution of dust extinction the SN population is expected to suffer.

Figure~\ref{k0_med:fig} also shows the distribution of $\gamma^1_V k_1$, which is associated with 
extinction corrections due to deviations away from the canonical $\kappa_1$ value.   The distribution has a long
negative tail and is peaked at its positive edge, and by construction has a mean of zero.
The implication is that while the bulk of supernovae have positive values associated with $R>1/\kappa_1$, there is a tail
of negative values associated with $R<1/\kappa_1$.  The plot of   $\gamma^0_V k_0$ versus $\gamma^1_V k_1$  shown in Figure~\ref{kk:fig} shows that
the positive edge in $\gamma^1_V k_1$ persists over the full range of  $\gamma^0_V k_0$. On the other hand, lower values of $\gamma^1_V k_1$
occur at larger values of  $\gamma^0_V k_0$.
These findings are consistent with previous results:
\citet{2014ApJ...789...32B, 2015MNRAS.453.3300A} deduce a wide range of dust behavior $1.5<R^F<3$ encountered by the SN~Ia population.
\citet{2011ApJ...729...55F} and the above authors
find that supernovae with large extinction 
preferentially exhibit low $R^F$.

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=2.8in]{output11/gamma0_med.pdf}
   \includegraphics[width=2.8in]{output11/gamma1_med.pdf}
      \caption{ Histogram of
median values of Left: $\gamma^0_V k_0$, which is associated up to an offset with the $A^F_V$ of an $R^F \sim 1/\kappa_1$ dust model; Right: $\gamma^1_V k_1$,
which  is associated with extinction corrections due to deviations away from the canonical $\kappa_1$ value.
   \label{k0_med:fig}}
\end{figure}

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=5.2in]{output11/kk.pdf}
      \caption{$\gamma^1_V k_1$ versus $\gamma^0_V k_0$.
   \label{kk:fig}}
\end{figure}
%
%The model parameters $E_{\gamma^0}(B-V)$ and  $E_{\gamma^1}(B-V)$ for the supernovae in our sample
%are projected onto the  \citetalias{1999PASP..111...63F} values of $E^F(B-V)$ and $A^F$, up to an additive constant:  these are shown in Figure~\ref{avebv:fig}.
%The points are confined to a tight locus around a line, with slope that corresponds to $R^F_V=2.24 \pm 0.16$.  
%The linear fit also produces the zeropoint, allowing us to determine individual $R^F_V$ for all supernovae,
%which are shown in Figure~\ref{avebv_synth:fig}.   The relative values of the projected parameters are similar to
%the native $R_V$, $A_V$, and $E(B-V)$  shown in Figure~\ref{avebv:fig}.
%
%\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
%   \centering
%   \includegraphics[width=2.8in]{output11/avebv_synth.pdf}
%   \includegraphics[width=2.8in]{output11/avrv_synth.pdf}
%    \caption{Left: Projections of our model parameters $E_{\gamma^0}(B-V)$ and  $E_{\gamma^1}(B-V)$ for the supernovae in our sample
%onto the  \citetalias{1999PASP..111...63F} dust-model plane.  Note that the error bars do not capture the strong
%covariance between the parameters. Right: $R^F_V$ for each supernova.
%   \label{avebv_synth:fig}}
%\end{figure}
%
